COLLISION RATES OF PLANETESIMALS NEAR MEAN-MOTION RESONANCES

### 2019-09-06 main.tex
Add discussion of fig 2

>>>>

The location of the mean motion resonances with Jupiter is most clearly visible when examining the semimajor axis-eccentricity distribution of the planetesimals. This is shown in figure \ref{fig:ae}, with the final snapshot from the CJ simulation shown on the left and EJ on the right. The solid vertical lines indicate the nominal locations of the mean motion resonances. Away from the resonance locations, the eccentricity dispersion grows via viscous stirring as energy from the Keplerian shearing of the disk is gradually transferred to random motions of planetesimals. The slight inward curving of the eccentricity peaks near the resonances is a consequence of the conservation of the Jacobi energy. As the semimajor axis of a planetesimal in MMR librates, the corresponding change in eccentricity is given by equation \ref{eq:tiss}.

In the EJ simulation, the eccentricity remains enhanced between the MMRs due to the secular forcing effect of Jupiter. This also has the consequence of making the eccentricity spikes due to the 5:2 and (what's the MMR at 3.6 AU?) more prominent. The reason for this is that the libration width of a resonance generally scales with the eccentricity of the particle being perturbed. In a secularly forced disk, the eccentricity of particles affected by resonance is larger, which increases the resonance width and allows a larger region of the disk to be affected by a given resonance. Also visible in the EJ snapshot in figure \ref{fig:ae} are eccentricity spikes that extend below the background eccentricity distribution. This is a clear sign that planetesimals in the MMRs are librating. The phase of the libration is set by the resonant argument (maybe I should add an equation for the resonant argument in section 2).
